---
title: "Statutory homelessness in England: April to June 2018"
output: html_notebook
---

```{r echo=FALSE, eval=FALSE, warning=FALSE}
getwd()
setwd("C:/Users/Moniczka/Documents/training/r/publication")
library(dplyr)
library(tidyr)
library(readxl)
library(haven)
library(lubridate)
library(stringr)
library(readr)
library(ggplot2)
library(ggrepel)
library(ggmosaic)
library(vcd)
library(forcats)
library(RColorBrewer)
library(scales)

Sys.setenv(TZ="Europe/London")

```{r echo=FALSE, eval=FALSE, warning=FALSE}
figure1_data=read_csv("Figure1.csv", skip=1)
View(figure1_data)
```
```{r echo=FALSE, eval=FALSE, warning=FALSE}
figure1_data$Initial_assessments=str_wrap(figure1_data$Initial_assessment_of_homeless_duties_owed, width=38)
figure1_data$Initial_assessments
```

```{r echo=FALSE, eval=FALSE, warning=FALSE}
ggplot(data = figure1_data, aes(x = Initial_assessments, y = Number_of_households, fill=Region)) + geom_bar(stat="identity", width=0.6) + theme_minimal() + scale_fill_brewer(palette="Paired") + coord_flip() + xlab("") +ylab("number of households") + theme(legend.position="top") + scale_x_discrete(limits=c("Not threatened with homelessness\nwithin 56 days", "Homeless-relief duty owed", "Threatened with homelessness-\nprevention duty owed")) + guides(fill=guide_legend(title=NULL, reverse=TRUE)) + theme(panel.grid.minor.y=element_blank(), panel.grid.major.y=element_blank()) + scale_y_continuous(labels = comma, limits = c(0, 35000)) + theme(axis.title.x = element_text(size=20, hjust=1), axis.text.x  = element_text(size=28)) + theme(axis.text.y  = element_text(size=28)) + theme(legend.text = element_text(size=28))
```
```{r echo=FALSE}
ggsave("figure1.jpg", plot = last_plot(), scale = 1, width = 13.33334, height = 8.88889, dpi = 72, limitsize = TRUE)
```

```{r echo=FALSE, eval=FALSE, warning=FALSE}
figure4_data=read_csv("Figure4.csv", skip=1)
View(figure4_data)
```

```{r echo=FALSE, eval=FALSE, warning=FALSE}
ggplot(data = figure4_data, aes(x = Quarter, y = Number_of_households, group=1)) + geom_line(colour="#2171B5", size=3) + theme_minimal() + xlab("") + ylab("number of households") + theme(panel.grid.minor.x=element_blank(), panel.grid.major.x=element_blank()) + scale_y_continuous(labels = comma, limits=c(0, 40000)) + theme(axis.title.y = element_text(hjust = 1, size=20), axis.text.x  = element_text(angle=90, size=26, colour=c("black", "transparent", "transparent", "transparent"))) + theme(axis.text.y  = element_text(size=28))
```
```{r echo=FALSE}
ggsave("figure4.jpg", plot = last_plot(), scale = 1, width = 13.33334, height = 8.88889, dpi = 72, limitsize = TRUE)
```
